\texttt{ggmatplot}: An R package for data visualization on wide-format data

### 2022-05-15 Paper/paper.Rmd
update paper with package and vignette source

The `ggmatplot`, built upon `ggplot2`, is an R-package that allows quick plotting across the columns of matrices or data with the result returned as a `ggplot` object. The package is inspired by the function `matplot()` in the core R `graphics` system -- as such, `ggmatplot` may be considered as a `ggplot` version of `matplot`, with the benefits of customising the plots as any other `ggplot` objects via `ggplot2` functions, as well as offering several other plotting types that are not immediately available from `matplot` directly e.g., comparative violin plots.

@@

The `ggmatplot` R-package provides a solution to a common friction encountered when wanting to quickly plot multivariate data, where the primary interest is mapping the column names as an aesthetic element. While an important start, we also acknowledge that solution provided is a recipe-driven approach, where the user can only produce plot types as many there are included in the `plot_type` option. Future developments of the package could benefit from using a grammar approach, like in @Wilkinson2005-oz and @Wickham2010-kt, where plot types can be extensible.

>>>>

The `ggmatplot`, built upon `ggplot2`, is an R-package that allows quick plotting across the columns of matrices or data with the result returned as a `ggplot` object. The package is inspired by the function `matplot()` in the core R `graphics` system -- as such, `ggmatplot` may be considered as a `ggplot` version of `matplot`, with the benefits of customising the plots as any other `ggplot` objects via `ggplot2` functions, as well as offering several other plotting types that are not immediately available from `matplot` directly e.g., comparative violin plots. The `ggmatplot` package is available on the Comprehensive R Archive Network (CRAN) with the latest developmental source code available at \url{https://github.com/xuan-liang/ggmatplot}.

@@

The `ggmatplot` R-package provides a solution to a common friction encountered when wanting to quickly plot multivariate data, where the primary interest is mapping the column names as an aesthetic element. While an important start, we also acknowledge that solution provided is a recipe-driven approach, where the user can only produce plot types as many there are included in the `plot_type` option. Future developments of the package could benefit from using a grammar approach, like in @Wilkinson2005-oz and @Wickham2010-kt, where plot types can be extensible. The latest developmental source code can be found at  Further examples can be found at \url{https://xuan-liang.github.io/ggmatplot/}.

### 2022-05-15 Paper/paper.tex
update paper with package and vignette source

The \texttt{ggmatplot}, built upon \texttt{ggplot2}, is an R-package
that allows quick plotting across the columns of matrices or data with
the result returned as a \texttt{ggplot} object. The package is inspired
by the function \texttt{matplot()} in the core R \texttt{graphics}
system -- as such, \texttt{ggmatplot} may be considered as a
\texttt{ggplot} version of \texttt{matplot}, with the benefits of
customising the plots as any other \texttt{ggplot} objects via
\texttt{ggplot2} functions, as well as offering several other plotting
types that are not immediately available from \texttt{matplot} directly
e.g., comparative violin plots.

@@

The \texttt{ggmatplot} R-package provides a solution to a common
friction encountered when wanting to quickly plot multivariate data,
where the primary interest is mapping the column names as an aesthetic
element. While an important start, we also acknowledge that solution
provided is a recipe-driven approach, where the user can only produce
plot types as many there are included in the \texttt{plot\_type} option.
Future developments of the package could benefit from using a grammar
approach, like in Wilkinson (2005) and Wickham (2010), where plot types
can be extensible.

>>>>

The \texttt{ggmatplot}, built upon \texttt{ggplot2}, is an R-package
that allows quick plotting across the columns of matrices or data with
the result returned as a \texttt{ggplot} object. The package is inspired
by the function \texttt{matplot()} in the core R \texttt{graphics}
system -- as such, \texttt{ggmatplot} may be considered as a
\texttt{ggplot} version of \texttt{matplot}, with the benefits of
customising the plots as any other \texttt{ggplot} objects via
\texttt{ggplot2} functions, as well as offering several other plotting
types that are not immediately available from \texttt{matplot} directly
e.g., comparative violin plots. The \texttt{ggmatplot} package is
available on the Comprehensive R Archive Network (CRAN) with the latest
developmental source code available at
\url{https://github.com/xuan-liang/ggmatplot}.

@@

The \texttt{ggmatplot} R-package provides a solution to a common
friction encountered when wanting to quickly plot multivariate data,
where the primary interest is mapping the column names as an aesthetic
element. While an important start, we also acknowledge that solution
provided is a recipe-driven approach, where the user can only produce
plot types as many there are included in the \texttt{plot\_type} option.
Future developments of the package could benefit from using a grammar
approach, like in Wilkinson (2005) and Wickham (2010), where plot types
can be extensible. The latest developmental source code can be found at
Further examples can be found at
\url{https://xuan-liang.github.io/ggmatplot/}.
